### 2021-06-09 paper/model_validation.tex
Add age group and state fit back in.
Add fitness plot with single simulation lines. Fix month in reference.

\begin{figure}[ht]
\centering
  % \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
\caption{Simulated and Empirical Infections}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates.}
\label{fig:aggregated_fit2}
\end{figure}

\begin{figure}[ht]
\centering
  % \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/age_group_rki/full_combined_baseline_new_known_case}
\caption{Simulated and Empirical Infections by Age Group}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different age groups.}
\label{fig:age_group_fit}
\end{figure}

\begin{figure}[ht]
\centering
  % \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/state/full_combined_baseline_new_known_case}
\caption{Simulated and Empirical Infections by Federal State}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different federal states.}
\label{fig:state_fit}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
  \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case_with_single_runs}
\caption{Simulated and Empirical Infections}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates.}
\label{fig:aggregated_fit2}
\end{figure}

\begin{figure}[ht]
\centering
  \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/age_group_rki/full_combined_baseline_new_known_case}
\caption{Simulated and Empirical Infections by Age Group}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different age groups.}
\label{fig:age_group_fit}
\end{figure}

\begin{figure}[ht]
\centering
  \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/state/full_combined_baseline_new_known_case}
\caption{Simulated and Empirical Infections by Federal State}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different federal states.}
\label{fig:state_fit}
\end{figure}
